---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{yifanpackage tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(yifanpackage)
```

```{r}
linear_regression(mtcars, "mpg", c("wt", "hp", "qsec"))
```

# Function Overview
1. This linear regression function helps to calculate the relative statistical values of linear regression.
It returns a list of relative statistical values of linear regression by entering three inputs, which include
the data, dependent variable and independent variables.

2. The first input data is just any complete data including several variables, which is the basis for extracting
dependent and independent variables. The second input is dependent variable, which is a variable going to measure in our study and depends on the independent variables. The third input are independent variables, which are variables in a model used to forecast the outcome of dependent variable based on their values.

3. For the example above, I have used the self-contained data in R named "mtcars". I have extracted the dependent
variable named "mpg" and the independent variables names "wt", "hp" and "qsec" from the data. After that, I have 
calculated the coefficients estimates, standard errors of coefficients, t values of coefficients, mean square error,
residual standard error, coefficient of determination, f value, p value, and confidence intervals of coefficients.
The function returns a list of these statistical values as the output.

